Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-02 outputs/paper/paper.qmd
Removed voting locations portion

#read in cleaned data #
cleaned_voter_statistics <- read.csv(here::here("inputs/data/cleaned_voter_statistics.csv"))
show_col_types = FALSE

cleaned_voting_locations <- read.csv(here::here("inputs/data/cleaned_voting_locations.csv"))
show_col_types = FALSE
```

@@

### Election Voting Locations
This dataset, published by the City Clerk's Office [@VotingLocations] highlights all polling locations and subdivisions, on a ward-by-ward basis from the 2022 municipal election. This data was last refreshed on November 2, 2022 and captured for this paper on May 21, 2023. The polling locations account for Advance Vote, election day, and Mail In Voting. One subdivision in a ward is equivalent to one polling location, based on geography. In each ward, subdivision 97 accounts for Mail In Voting, while subdivisions 98 and 99 are designated Advance Vote locations. Voters can request a Mail In ballot, go to one of the two Advance Vote locations during the designated days, or vote at their assigned subdivision on election day (for example: Ward 11, Subdivision 11).

```{r}
#| message: false
#| echo: false
#| label: tbl-cleaned_voting_location
#| tbl-cap: Sample of Cleaned Voting Locations Data

# code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
# & https://tellingstorieswithdata.com/20-r_essentials.html 
head (cleaned_voting_locations, 5) |>
  select(point_short_code, point_long_code, address_full) |>
  kable(
    col.names = c("Subdivision", "Ward & Subdivision", "Address"),
  booktabs = TRUE
  )

@@

For the purpose of this paper, I did not include the Advance Vote and Mail In Voting subdivisions when counting the total number of subdivisions per ward. Firstly, there are only two Advance Vote locations distributed across every ward, meaning residents have to be motivated to travel farther away from their home to cast their ballot. Secondly, Mail In Voting requires applying online through Toronto Elections and then returning the completed Mail In Voting package by dropping it in a Canada Post mailbox or hand delivering it to one of the Toronto Elections drop boxes at select locations. Voters need to be more organized and motivated to vote in advance of election day.

>>>>

#read in cleaned data #
cleaned_voter_statistics <- read.csv(here::here("inputs/data/cleaned_voter_statistics.csv"))
show_col_types = FALSE
```

@@

@@

For the purpose of this paper, I included the Advance Vote and Mail In Voting subdivisions when counting the total number of subdivisions per ward. Firstly, there are only two Advance Vote locations distributed across every ward, meaning residents have to be motivated to travel farther away from their home to cast their ballot. Secondly, Mail In Voting requires applying online through Toronto Elections and then returning the completed Mail In Voting package by dropping it in a Canada Post mailbox or hand delivering it to one of the Toronto Elections drop boxes at select locations. Voters need to be more organized and motivated to vote in advance of election day.
